Kung Faux Pandas \\ \large Alternative Facts for Privacy Preservation

### 2018-05-08 paper/seth.tex
Auto Update from local Sharelatex

>>>>

Need something smilar to this - part of our 
"in the U.S., the Privacy Rule of the Health Insurance Portability and Accountability Act (HIPAA)  outlines two policies for protecting anonymity, namely Safe Harbor, and Expert Determination. The first of these policies enumerates eighteen direct identifiers that must be removed from data, prior to their dissemi- nation, while, according to the Expert Determination policy, an expert needs to certify that the data to be disseminated pose a low privacy risk before the data can be shared with external parties."
